Cycle Route Uptake and Scenario Estimation (CRUSE): an open and nationally scalable approach for strategic cycle network planning tool development

### 2024-03-22 paper.qmd
New images for Figure 1

::: {#fig-dublin}
![](images/paste-1.png)

![](images/paste-3.png)

Illustration of the density of route networks generated by the CRUSE Tool for Dublin City and surroundings (top) and rural County Mayo on the West coast of Ireland.
Source: CRUSE Tool, available at <https://cruse.bike/>.
:::

@@

::: {#fig-user-stories}

![](images/mermaid-figure-1.png)

Hypothetical user stories for the CRUSE Tool illustrating that it can be used in different ways by different user groups.

:::

>>>>

::: {#fig-dublin}
<!-- ![](images/paste-1.png) -->
![](images/paste-8.png)
:::

<div>

<!-- ![](images/paste-3.png) -->
![](images/paste-9.png)

Illustration of the density of route networks generated by the CRUSE Tool for Dublin City and surroundings (top) and rural County Mayo on the West coast of Ireland (botton).
Source: CRUSE Tool, available at <https://cruse.bike/>.

</div>

@@

::: {#fig-user-stories}
![](images/mermaid-figure-1.png)

Hypothetical user stories for the CRUSE Tool illustrating that it can be used in different ways by different user groups.
:::
